PANCHANGE_data_preprocessing

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
GAD baseline, retro and prepan missingness per person chunks

#PHQ - prepanspective
PHQ Missingness NAs per person - count and percentages
```{r PHQ prepanspective missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_phq_prepan =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at prepanline
           %in%
             phq.items_prepan]
        )
    )
  )

@@

Missingness per item
```{r Missingness per item}
dat.no.sex.no.gender.no.age.no.ibd.miss <- as.data.frame(colnames(dat.no.sex.no.gender.no.age.no.ibd[,PHQ.items]))
colnames(dat.no.sex.no.gender.no.age.no.ibd.miss) <- "Items"
dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss <- colSums(is.na(dat.no.sex.no.gender.no.age.no.ibd[,PHQ.items]))
dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss.pc <- dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss/nrow(dat.no.sex.no.gender.no.age.no.ibd[,PHQ.items])
table(dat.no.sex.no.gender.no.age.no.ibd.miss$Items, dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss.pc)
summary(dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss.pc)

ggplot(data = dat.no.sex.no.gender.no.age.no.ibd.miss,
       aes(x = Items, y = item.miss.pc)) +
  geom_point() +
  labs(title = "GLAD: PHQ",
    y ="Missingness per item") +
  theme_minimal() +
  coord_flip()
```

```{r count of people missing a number of items}
table(dat.no.sex.no.gender.no.age.no.ibd$na.per.person.phq)
```

>>>>

#PHQ - prepandemic
PHQ Missingness NAs per person - count and percentages
```{r PHQ prepan missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_phq_prepan =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at prepanline
           %in%
             phq.items_prepan]
        )
    )
  )

@@

Count for PHQ baseline, retrospective, and prepandemic missingness per person
```{r count of people missing a number of items for PHQ}
#baseline
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base)
#retrospective
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_retro)
#pre-pandemic
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_prepan)
```

#GAD - baseline
GAD Missingness NAs per person - count and percentages
```{r gad basline missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_gad_base =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at baseline
           %in%
             gad.items_base]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base) #have a look at the frequency

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_gad_base = 
      na_per_person_gad_base/7 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_base)
```

#gad - retrospective
gad Missingness NAs per person - count and percentages
```{r gad retrospective missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_gad_retro =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at retroline
           %in%
             gad.items_retro]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro) #have a look at the frequency

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_gad_retro = 
      na_per_person_gad_retro/7 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_retro)
```

#gad - prepandemic
gad Missingness NAs per person - count and percentages
```{r gad prepan missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_gad_prepan =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at prepanline
           %in%
             gad.items_prepan]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan) #have a look at the frequency

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_gad_prepan = 
      na_per_person_gad_prepan/7 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_prepan)
```

Count for gad baseline, retrospective, and prepandemic missingness per person
```{r count of people missing a number of items for gad}
#baseline
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base)
#retrospective
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro)
#pre-pandemic
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan)
```
